Extending Graphical Representations for Compact Closed Categories with Applications to Symbolic Quantum Computation

### 2008-05-02 papers/reasoning-graphically/paper.tex
slight tweak of pic and added sentence about !-box needing to be not k-tuples.
git-svn-id: https://isaplanner.svn.sourceforge.net/svnroot/isaplanner/trunk/quantomatic@1473 f8f375fb-4f10-0410-8d47-b6fbdc7ca053

\item[merge]: combines two !-boxes, $B_1$ and $B_2$ into a single
  larger !-box $B_1 \cup B_2$.
\end{description}

\begin{figure}[t]
$$\begin{array}{ccccccc}
\inlinegraphic{3.8em}{bbox-ex1} & 
\frac{\leq}{copy} & \inlinegraphic{3.8em}{bbox-ex2}  & 
\frac{\leq}{merge} & \inlinegraphic{3.8em}{bbox-ex3}  & 
\frac{\leq}{drop} & \inlinegraphic{3.8em}{bbox-ex4}
\end{array}$$
\label{fig:bang-box-example}\caption{An illustration of !-box graph
  matching using the !-box operations. This involves first copying
  !-box $i_0$ twice, then merging $i_0$ and $i_1$ and finally dropping
  $i_3$.}
\end{figure}

@@

Observe that an instance of a !-box graph is defined by pairing each
!-box with the natural number that defines how many copies are made of
it. Thus $\binterp{G}$ is isomorphic to the set of $k$-tuples of
natural numbers, where $k$ is the number of !-boxes.

@@

>>>>

\item[merge]: combines two !-boxes, $B_1$ and $B_2$ into a single
  larger !-box $B_1 \cup B_2$. To ensure that copying after merging
  commutes with copying before, merging is restricted to !-boxes which
  do not have an edge between their nodes.
\end{description}

\begin{figure}[t]
$$\begin{array}{ccccccc}
\inlinegraphic{4em}{bbox-ex1} &  
\stackrel{\leq}{\stackrel{\ }{\small{copy}}} 
& \inlinegraphic{4em}{bbox-ex2}  & 
\stackrel{\leq}{\stackrel{\ }{\small{merge}}} 
& \inlinegraphic{4em}{bbox-ex3}  & 
\stackrel{\leq}{\stackrel{\ }{\small{drop}}} 
& \inlinegraphic{4em}{bbox-ex4}
\end{array}$$ 
\label{fig:bang-box-example}\caption{An illustration of !-box graph
  matching using the !-box operations. This involves first copying
  !-box $i_0$ twice, then merging $i_0$ and $i_1$ and finally dropping
  $i_3$.}
\end{figure}

@@

Observe that every concrete instance of a !-box graph can be defined
by pairing each !-box with the natural number that defines how many
copies are made of it. Thus $\binterp{G}$ is isomorphic to the set of
$k$-tuples of natural numbers, where $k$ is the number of !-boxes.

@@

The need for the !-box matching operation, rather than using a direct
$k$-tuple interpretation, is to allow matching between !-box graphs,
and thus to provide a mechanism for derived rules.
